Transient brightenings observed with multiple instruments

### 2021-11-01 Paper1.tex
Updates from Overleaf

% Nick stuff, feel free to change at will, I was just getting my thoughts out.
\subsection{ALMA}
\paragraph{ALMA background} The Atacama Large Millimeter Array (ALMA) is a radio interferometer with current frequency coverage spanning 84 to 950 GHz. ALMA is constituted of 66 telescope dishes, 54 with a diameter of 12 meters, and 12 with a diameter of 7 meters. These 66 dishes are arranged as such to ensure that ALMA had suitable sensitivity to large scale diffuse emission, this is aided by the high density of centrally located dishes, and excellent resolution to small scale features, this is achieved with the dishes at high distance. The ALMA observations presented in this work were in the ALMA observing Band 3, which corresponds to a central frequency of 100 GHz, and a total bandwidth of 18 GHz about that central frequency. At this frequency and array configuration, our approximate resolution is 2$\arcsec$ on the sky. Our integration time used was 2 seconds and the entire observation, including the target field and calibrators, lasted for 1.03 hours.

\paragraph{ALMA calibration}
\paragraph{ALMA self-calibration}
\paragraph{ALMA issues with phase-center}

>>>>

\subsection{ALMA}
\paragraph{ALMA background} The Atacama Large Millimeter Array (ALMA) is a radio interferometer with current frequency coverage spanning 84 to 950 GHz \citep{2009WootenThompson_ALMA}. ALMA is constituted of 66 telescope dishes, 54 with a diameter of 12 meters, and 12 with a diameter of 7 meters. These 66 dishes are arranged as such to ensure that ALMA has suitable sensitivity to large-scale diffuse emission, achieved by the high density of centrally located dishes, and excellent resolution to small scale features, achieved with the dishes at long distance. The ALMA observations presented in this work were in the ALMA observing Band 3, which corresponds to a central frequency of 100 GHz, and a total bandwidth of 18 GHz about that central frequency. At this frequency and array configuration, our approximate resolution is 2$\arcsec$ on the sky. Our integration time is 2 seconds, and the entire observation, including the target field and calibrators, had a duration of 1.03 hours.

\paragraph{ALMA calibration} The ALMA Band 3 data were cross-calibrated using the standard ALMA pipeline Cycle 4 version\footnote{For a thorough description of the tasks and philosophy see: ALMA Pipeline Team, 2017, ALMA Science Pipeline User’s Guide, ALMA Doc 4.13v2.0}. in CASA version 4.7.2 \citep{casa}. The observations were taken with the strong millimeter source, J2253+1608, approximately 6.5 Jy in ALMA Band 3, used for the bandpass and flux calibration, and the strong millimeter source, QSO\_B0003-066, approximately 2 Jy in ALMA Band 3, used for the phase cross calibration. The initial cross-calibration eliminated 4 dishes due to unreasonably elevated system temperatures, and produced images of a reasonable quality, but still suffering from some poor calibration artifacts.

\paragraph{ALMA self-calibration} In order to improve the fidelity of our images, we then phase-only self-calibrate the data. The phase-only self-calibration is an iterative process in which we took the following steps. We first produce a cleaned map of the data, but we clean only to a relatively modest level, to ensure all flux captured in the clean model is real. We then do a phase-only gaincal over a large time-range, in the first iteration this was a scan length (5 minutes), using the clean model, and apply this calibration to the data. We do this process iteratively, where in each iteration we clean to a lower flux threshold, and shorten the time-range used in the phase-only self calibration. We terminate the process when there is no decrease in out-of-field r.m.s. noise, and the image shows little-to-no improvement. The improvements caused by this process are the elimination of PSF pattern relics in the image, and the sharpening of the image, which is why this process if often compared to the effect of focusing a telescope or microscope.

\paragraph{ALMA issues with phase-center}
